---
title: "Final exam part B: descriptive analysis"
author: Pablo Barbera
---

The goal of this second part of the assignment is to analyze the datasets you just created in order to answer a set of descriptive questions. Your answer to the questions will offer important context towards the overall research question:  __Why is there so much negativity on Facebook comments about politics?__

For each item below, you should write code with any statistical or graphical analysis that you consider appropriate, and then answer the question.

1. First of all, how much negativity is there on the comments of pages by U.S. legislators? In other words, what proportion of comments are negative?

```{r}

```

2. How much variation is there in the level of negativity that legislators see on their Facebook pages? Which are the legislators with the highest and lowest proportion of negative comments?

```{r}

```

3. How did negativity evolve over time during the period of analysis? Do you identify any particular days or periods during which negativity spiked? Can you explain why?

```{r}

```

4. Are there any other variables in the dataset that could help you measure negativity? If so, do you find similar results to questions 2 and 3 when you use that other signal?

```{r}

```

5. (Note: this question is hard!) What proportion of comment threads have at least one negative comment?

```{r}

```


