---
title: 'Part A: Writing more efficient code'
author: "Pablo Barbera"
---

The purpose of this set of exercises is to practice writing more efficient code. You will be presented with a series of code chunks that I'm honestly ashamed to have written! Using a combination of vectorized functions and more efficient handling of memory, try to see how fast you can make it run. Be creative! 

You will be marked based on how much your code is able to reduce the running time of my code, while still being easy to read.

Here's the dataset we'll be using for this challenge -- a random sample of 10,000 tweets related to the 2014 EP elections in the UK. To make it a bit more challenging, we'll multiply the size of the dataset by 5.

```{r}
d <- read.csv("/Users/ctwo/Desktop/R/UK-tweets.csv", stringsAsFactors=F)
d <- rbind(d, d, d, d, d)
d <- na.omit(d)
```


## 1. Count how many tweets are classified as impolite:

```{r}
func1 <- function(){
  
  count <- 0
  
  for (i in 1:nrow(d)){
    if (d$polite[i]=="impolite"){
      count <- count + 1
    }
  }
  return(count)
}

system.time(func1())

```

Your solution here:

```{r}
func2 <- function(){
  return(length(which(d$polite == "impolite")))
}
system.time(func2())
```

## 2. Count what proportion of tweets are classified as engaging:

```{r}
func1 <- function(){
  
  engaging.count <- 0
  for (i in 1:nrow(d)){
    if (d$communication[i]=="engaging"){
      engaging.count <- engaging.count + 1
    }
  }
  total.tweets <- 0
  for (i in 1:nrow(d)){
    total.tweets <- total.tweets + 1
  }
  prop <- engaging.count/total.tweets
  return(prop)
}

system.time(func1())

```

Your solution here:

```{r}
func2 <- function(){
  return((length(which(d$communication=="engaging")))/nrow(d))
}
system.time(func2())
```

## 3. Count how many tweets mention Merkel:

```{r}
func1 <- function(){
  brexit_tweets <- c()
  for (i in 1:nrow(d)){
    if (grepl("brexit", d$text[i], ignore.case=TRUE)==TRUE){
      brexit_tweets <- c(brexit_tweets, i)
    }
  }
  return(length(brexit_tweets))
}
system.time(count <- func1())
```

Your solution here:

```{r}
func2 <- function(){
  return(length(grep("brexit",d$text,ignore.case = TRUE)))
}
system.time(func2())
```

## 4. Take a random sample of 200 tweets that are classified as "impolite"

```{r}
func1 <- function(){
  
  # sample random uniform number
  d$random <- runif(nrow(d))
  # sort by this random number
  dd <- d[order(d$random),]
  # loop over rows using 'while'
  smp <- data.frame()
  i <- 1
  while (nrow(smp)<200){
    if (d$polite[i]=="impolite"){
      smp <- rbind(smp, d[i,])
    }
    i <- i + 1
  }
  return(smp)

}

system.time(func1())

```

Your solution here:

```{r}
func2 <- function(){
  d$random <- runif(nrow(d))
  dd <- d[order(d$random),]
  smp <- data.frame()
  smp <- rbind(smp,d[(which(d$polite == "impolite"))[0:200],])
  return (smp)
}
system.time(func2())
```





# 5. Compute the average number of followers for tweets that are impolite and polite

```{r}
func1 <- function(){
  # average number of followers for impolite tweets
  #append the follower,
  impolite.follower.counts <- c()
  for (i in 1:nrow(d)){
    if (d$polite[i]=="impolite"){
      impolite.follower.counts <- c(impolite.follower.counts, d$followers_count[i])
    }
  }
  #add up
  impolite.follower.sum <- 0
  for (i in 1:length(impolite.follower.counts)){
    impolite.follower.sum <- impolite.follower.sum + impolite.follower.counts[i]
  }
  #calculate total
  impolite.tweets.total <- 0
  for (i in 1:nrow(d)){
    if (d$polite[i]=="impolite"){
      impolite.tweets.total <- impolite.tweets.total + 1
    }
  }
  impolite.follower.mean <- impolite.follower.sum / impolite.tweets.total
  
  
  
  # average number of followers for polite tweets
  polite.follower.counts <- c()
  for (i in 1:nrow(d)){
    if (d$polite[i]=="polite"){
      polite.follower.counts <- c(polite.follower.counts, d$followers_count[i])
    }
  }
  polite.follower.sum <- 0
  for (i in 1:length(polite.follower.counts)){
    polite.follower.sum <- polite.follower.sum + polite.follower.counts[i]
  }
  polite.tweets.total <- 0
  for (i in 1:nrow(d)){
    if (d$polite[i]=="polite"){
      polite.tweets.total <- polite.tweets.total + 1
    }
  }
  polite.follower.mean <- polite.follower.sum / polite.tweets.total  

  return(c(impolite.follower.mean, polite.follower.mean,
           polite.follower.sum,polite.tweets.total))
  # 2473.324 108165.132   1095.000  118440820(followers)

}

system.time(func1())

```

Your solution here:

```{r}
func2 <- function(){
  imp.counter <- 0
  imp.followers <- 0
  pol.followers <- 0
  
  for (i in (1:nrow(d))){
    if(d$polite[i] == "impolite"){#if ture -> impolite
      imp.counter <- imp.counter +1
      imp.followers <- imp.followers + d$followers_count[i]
    }
    else{
      pol.followers <- pol.followers + d$followers_count[i]
    }
  }
  return(c(imp.followers/imp.counter, pol.followers/(nrow(d)-imp.counter)))
}

system.time(func2())
```

# 6. Compute the proportion of tweets mentioning Merkel, Farage, Labour, Europe or Coburn (ignoring capitalization) that are impolite.

```{r}
func1 <- function(){
  # creating new DF with tweets that mention one of the keywords
  df <- data.frame()
  keywords <- c("Brexit", "farage", "labour", "europe", "coburn")
  for (word in keywords){
    matches <- grep(word, d$text, ignore.case=TRUE)
    df <- rbind(df, d[matches,])
  }#df6675
  df <- df[!duplicated(df$text),]
  
  # counting proportion of impolite tweets
  impolite.count <- 0
  for (i in 1:nrow(d)){
    if (d$polite[i]=="impolite"){
      impolite.count <- impolite.count + 1
    }
  }
  #impolite 1095
  prop <- impolite.count/nrow(df)
  return(prop)

}#0.8809332 #0.662 user

system.time(func1())

```

Your solution here:

```{r}
func2 <- function(){
  keywords <- c("Brexit", "farage", "labour", "europe", "coburn")
  df <- data.frame()
  df.list <-list()
  
  for (i in 1:(length(keywords))){
    match_rows <- grep(keywords[i],d$text,ignore.case = TRUE)
    df.list[[i]] <- data.frame(d[match_rows,])
  }
  df<- do.call(rbind,df.list)#6675
  df <- df[!duplicated(df$text),]#1243
  
  return( (length(which(d$polite=="impolite")))/nrow(df))
}


system.time(func2())
```

